% LaTeX resume using res.cls
\documentclass[margin,11pt]{res}
\usepackage{hyperref}   % ability to create clickable hyperlinks
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\oddsidemargin=-0.4in
\textwidth=5.9in % set width of text portion
\textheight=792pt
\voffset=-0.5in

%\setlength{\tabcolsep}{2pt}

\begin{document}
% Name centered over entire width of resume:
\moveleft.5\hoffset\centerline{\LARGE\bf Adrian H. Padin}
% Horizontal line the whole width of resume:
\vspace{-6pt}
%\moveleft.5\hoffset\vbox{\hrule width\resumewidth height 1pt}
\moveleft\hoffset\vbox{\hrule width 7.2in height 1pt}
% Address centered over entire width of resume:
\moveleft.5\hoffset\centerline{331 Pemberton Park Ln, Frederick, MD 21703}
\moveleft.5\hoffset\centerline{padin.adrian@gmail.com $\cdot$ (440) 724-9273}

\vspace{-20pt}
\begin{resume}

\section{SUMMARY}
Seeking a full-time software engineering position.
I have 4+ years experience in embedded software development in C, C++, and Rust;
and 4 years experience in ERP business software using Wolfram Language and
Mathematica.
I am a motivated and hard-working individual with a desire to make a difference
and collaborate with like-minded people.

\section{WORK EXPERIENCE}

\textbf{Hubbell, Inc. / Aclara LLC} \hfill Solon, OH\\
\textsl{Senior Firmware Engineer} \hfill July 2023 - Present
\begin{itemize}
    \itemsep -2pt
    \item Hubbell, Inc. is a global company that provides electrical equipment
          and infrastructure for consumers and utility providers.
          Aclara is a division of Hubbell that specializes in metering
          infrastructure for gas, water, and electrical utility systems.
    \item Served as one of the primary developers for Aclara's next generation
          line of meter data collection and monitoring system.
          Developed firmware for the Base Station, the device that collects and
          aggregates meter data for all meters in the surrounding area.
          Meter data is collected wirelessly with a proprietary RF protocol and then
          sent over an ethernet or cell connection to a cloud server.
    \item Primary developer for the part of the Base Station firmware which
          implemented the application layer of the proprietary RF protocol, focused
          on collecting and parsing gas and water meter data.
    \item Developed code primarily in Rust, which I had no experience with prior
          to starting this project. I was able to quickly learn the language in
          just a few weeks before I was ready to start contributing.
\end{itemize}

\textbf{Wolfram Research, Inc.} \hfill Champaign, IL\\
\textsl{Wolfram Language Developer, ERP Business Software} \hfill April 2019 - July 2023
\begin{itemize}
    \itemsep -2pt
    \item Wolfram Research Inc. develops software which enables students,
          researchers, and businesses to perform computation and analyze data
          for a variety of use cases. Their main products are Mathematica and
          Wolfram Alpha, which both make use of the Wolfram programming language.
    \item As part of a team of 6+ developers, created a custom ERP system to
          handle order processing and product licensing for Mathematica, Wolfram
          Alpha, and every other Wolfram product. This system made use of
          EntityLink, a framework we designed which can generate both a database
          schema and an API for creating, updating, and retrieving structured
          data using a single set of configuration files.
    \item Made significant code and infrastructure contributions, including
          developing a job queuing system to handle asynchronous tasks in a
          timely manner, implemented using the same EntityLink framework and
          Wolfram language code.
\end{itemize}

\vspace{-10pt}
\textbf{Control-Tec, LLC.} \hfill Allen Park, MI\\
\textsl{C++ Software Developer, Embedded Linux} \hfill May 2017 - April 2019
\begin{itemize}
    \itemsep -2pt
    \item Developed next-generation automotive data collection software for a
          live data-processing application called CT-EDGE. This software
          collects data from the vehicle using broadcast CAN and standardized
          request formats including J1979 and UDS, and can analyze the data
          based on configurable triggers to send notifications and telemetry
          to a cloud server over a cellular connection.
    \item Gained extensive experience with the Legato embedded Linux IoT
          platform. The platform is similar to Android, where developers
          can create sandboxed "apps" that communicate through secure IPC.
          This allowed our team to improve security by separating
          functionalities such as vehicle data collection, cloud communication,
          and over-the-air firmware updates.
    \item Managed a small team of engineers to assist in software development
          and white-box testing.
\end{itemize}

\pagebreak

\vspace{-10pt}
\textbf{Merit Network, Inc.} \hfill Ann Arbor, MI\\
\textsl{Research Assistant, Data Analyst} \hfill May 2016 - May 2017
\begin{itemize}
    \itemsep -2pt
    \item Research assistant under Dr. Michalis Kallitsis, researching anomaly
          detection for early warnings of Distributed Denial-of-Service attacks
          and other malicious data-injection attacks.
    \item Assisted with a project to develop Machine Learning algorithms and
          tools to detect false data injection attacks on a smart electrical
          grid. The goal was to prevent an attacker from manipulating a
          homeowner's electricity usage. I wrote scripts to aggregate the data
          from various sensors, feed the it to the algorithm and interpret the
          results.
    \item Primary author on a research paper detailing an experiment conducted
          at a facility in Detroit, MI, to test the custom analysis software
          we had designed in a real-world environment. The paper was presented
          by Dr. Kallitsis at a conference for IoT Smart Grid applications.
\end{itemize}

\vspace{-10pt}
\textbf{Innovative Devices, Inc.} \hfill Bedford Hts., OH\\
\textsl{Software Engineering Intern} \hfill May 2015 - Sept 2015
\begin{itemize}
    \itemsep -2pt
    \item Assisted in research and development of the Mycestro wearable computer
          mouse and worked with a team of engineers to develop integration
          software in Python and Ruby for using the Mycestro as a 3D mouse.
    \item Wrote Python plugins to model rotations of simulated objects using
          matrix rotations and vector mathematics. Motion data from the Mycestro
          was then used to control these rotations.
%     \item Attended patent strategy and business development meetings, and gave
%           sales presentations to potential investors.
\end{itemize}

\vspace{-10pt}
\section{TECHNICAL SKILLS}
\textbf{Programming Languages:}\\
\vspace{-10pt}
\begin{itemize}
    \itemsep -2pt
    \item Proficient in C, C++, Rust, Python, and Mathematica / Wolfram Language.
    \item Comfortable with HTML, JavaScript, JSON, and Bash.
    \item Also worked with Ruby, PHP, C\#, and Java.
    \item Familiar with Object-Oriented and Functional design strategies.
    \item This resume was created with LaTeX.
          You can view the source files on my GitHub page (see bottom).
\end{itemize}

\vspace{-10pt}
\textbf{Software:}
\begin{itemize}
    \itemsep -2pt
    \item Git version control.
    \item Experienced with Jira/Atlassian and Azure DevOps for project management.
    \item Google Test (gtest) unit test framework.
    \item Linux and Windows user, especially Linux command line tools.
%     \item Many years of experience with Microsoft Word, Excel, and PowerPoint.
\end{itemize}

\vspace{-10pt}
\textbf{Hardware:}
\begin{itemize}
    \itemsep -2pt
    \item Designed custom PCBs using Eagle design software.
    \item Experienced with hand soldering PCBs and components.
\end{itemize}

\vspace{-10pt}
\section{EDUCATION}
% \sl will be bold italic in New Century Schoolbook (or any postscript font) and
% just slanted in Computer Modern (default) font
\textbf{University of Michigan} \hfill Ann Arbor, MI\\
B.S.E. in Computer Engineering \hfill May 2017\\
Minor in Music\\
GPA: 3.94/4.0\\
\vspace{-24pt}

\textbf{Relevant Coursework}\\
\vspace{-10pt}
\\
\vspace{-10pt}
\begin{tabular}{l l}
%    EECS 280: Electromagnetics I & PHYS 340: Waves, Heat, and Light\\
%    EECS 330: Electromagnetics II & EECS 320: Semiconductor Devices\\
%    EECS 351: Digital Signal Processing & EECS 475: Cryptography\\
%   EECS 473: Advanced Embedded Systems & (Senior Design Project)\\
    EECS 473: Advanced Embedded Systems & EECS 482: Operating Systems\\
    EECS 461: Embedded Control Systems & EECS 445: Machine Learning\\
    EECS 373: Microprocessor Programming & EECS 388: Computer Security\\
\end{tabular}

\pagebreak

\section{PERSONAL}
\textbf{University of Michigan Marching Band} \hfill Aug 2013 - May 2017\\
\textsl{Trumpet Player}\\
\textsl{Manager, MMB Merchandise Staff from 2014-2015}\\
\textsl{Treasurer, Tau Beta Sigma Honorary Band Society from 2015-2017}\\
\\
\textbf{Favorite Text Editor:} Visual Studio Code (GUI), Vim (terminal)\\
\textbf{Favorite Browser:} Firefox\\
\textbf{Hobbies:} Playing trumpet, building gadgets, video games

\section{WEBSITES}
\textbf{LinkedIn:}
\href{https://www.linkedin.com/in/adrian-padin-320a34a4}{https://www.linkedin.com/in/adrian-padin-320a34a4}\\
\textbf{Github (resume source code):}
\href{https://github.com/padinadrian/resume}{https://github.com/padinadrian/resume}\\

\vspace{10pt}
\moveleft.5\hoffset\centerline{\large\bf References available upon request}

\end{resume}
\end{document}
